Productivity estimation in waterfowl using a non-invasive method

### 2021-10-01 Code/Draft_ruddy_duck_productivity.Rmd
figure update

## Few words on the species {-}

@@

## Dichromatism characterization {-}

@@

## Time series {-}

@@

|Name|Description|
|:--|:----------------------------|
|$N_{t}$|Number of individuals in year $t$|
|$D_{t}$|Number of individuals removed in year $t$|
|$R_{t}$|Number of recruits in year $t$|
|$S_{t}$|Adult survival rate, i.e. proportion of breeder in year $t-1$ still alive in year $t$|
|$P_{t}$|Number of recruits in year $t$ produced per breeder in year $t - 1$|

@@

## Model {-}

@@

## Survival estimation {-}

@@

@@

@@

@@

(ref:MM1cap) Evolution of the size of the two Ruddy duck populations in light of the harvest pressure; on time periods without harvest, population growth rates can be estimated (slopes in red for the UK and in blue for France)

(ref:MM2cap) Evolution of the size of the two Ruddy duck populations in light of the data time series; on restricted time periods with available data, population growth rates can be estimated (slopes in red for the UK and in blue for France)

@@

(ref:R2cap) (A) Estimates of the population growth rate without harvest; two estimates were produced for the UK population because the growth rate dropped significantly when its size reached more than 1000 individuals; (B) Growth rate estimates, bars define the 95\\% confidence intervals

(ref:R3cap) (A) Estimates of the population growth rate on time intervals with data availability. This aims at producing survival estimates to discuss the reliability of the methods to estimate productivity; (B) Growth rate estimates, bars define the 95% confidence intervals

(ref:R4cap) (A) Average productivity estimates on the time intervals defined for survival analysis

>>>>

## The studied species

@@

## Dichromatism characterization

@@

## Data time series

@@

@@

## Model

@@

## Result validation using survival analysis

|Name|Description|
|:--|:----------------------------|
|$N_{t}$|Number of breeders in year $t$|
|$D_{t}$|Number of breeders removed in year $t$|
|$R_{t}$|Number of recruits in year $t$|
|$S_{t}$|Adult survival rate, i.e. proportion of breeder in year $t-1$ still alive in year $t$|
|$P_{t}$|Number of recruits in year $t$ produced per breeder in year $t - 1$|

@@

## Result validation by comparison to maximum productivity

@@

## Productivity estimates

@@

## Result validation using survival analysis

@@

(ref:MM1cap) Evolution of the size of the two Ruddy duck populations in light of the data time series; on restricted time periods with available data, population growth rates can be estimated (slopes in red for the UK and in blue for France)

(ref:MM2cap) Evolution of the size of the two Ruddy duck populations in light of the harvest pressure; on time periods without harvest, population growth rates can be estimated (slopes in red for the UK and in blue for France)

@@

(ref:R2cap) (A) Estimates of the population growth rate on time intervals with data availability. This aims at producing survival estimates to discuss the reliability of the methods to estimate productivity; (B) Growth rate estimates, bars define the 95% confidence intervals

(ref:R3cap) (A) Average productivity estimates on the time intervals defined for survival analysis; (B) Underlying average survival estimates

(ref:R4cap) (A) Estimates of the population growth rate without harvest; two estimates were produced for the UK population because the growth rate dropped significantly when its size reached more than 1000 individuals; (B) Growth rate estimates, bars define the 95% confidence intervals
